---
title: "WGNA_PSVD"
author: "Aishwarya"
date: "8/3/2022"
output: html_document
---



# Script and session info
Script name: WGCNA-PSVD.Rmd

Purpose of script: Using gene co-expression network to functionally analyse mRNA and miRNA expression trends in colon cancer progression 
Author: Aishwarya Iyer

Date Created: 03-08-2022

## Session info:
R version 3.10 
Platform: x86_64-w64-mingw32/x64 (64-bit)
Running under: Windows 10 x64 

# Set up environment
```{r}
#clear workspace and set string as factors to false
#rm(list=ls())
options(stringsAsFactors = F)

```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Install required packages
```{r,echo=FALSE}
#BiocManager::install("WGCNA")
##install devtools
#install.packages("devtools") #if needed
#install PANEV
#library("devtools")
#install_github("vpalombo/PANEV")
#BiocManager::install("clusterProfiler")
library(AnnotationDbi)
library(preprocessCore)
library(GO.db)
library(WGCNA)
library(rstudioapi)
library(dplyr)
library(biomaRt)
library(clusterProfiler)
#library(PANEV)
```


```{r}
setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
```


```{r}
#Import variant file
normalised_gene_expression<- read.delim("normalised-data.txt",header=TRUE)

#remove samples with missing gender information 
normalised_data = subset(normalised_gene_expression, select = -c(HNL07,HNL13, HNL14) )

#remove diseased sample (B09. 28015) as corresponding clinical data not available ( might have been a cirrhotic misdiagnosed case)
normalised_data = subset(normalised_data, select = -c(PSVD17))
 
```


```{r}
#import clinical data 

library(readxl)
clinical_data_intial <- read_excel("clinical_data_intial.xlsx")
View(clinical_data_intial) 


#remove samples with missing sex in clinical data 

clinical_1<-clinical_data_intial[-c(7,13,14),]
clinical_1<-clinical_1[1:28,]

rownames(clinical_1)<-colnames(normalised_data)


```




# check if there are samples with missing data
```{r}
gsg = goodSamplesGenes(normalised_data, verbose = 3);
gsg$allOK

# remove rows with all low expression
combined.filtered <- normalised_data[rowSums(normalised_data) > 0.5, , drop=TRUE]
combined.filtered <- as.data.frame(t(as.matrix(combined.filtered)))

#combined.filtered_selected<-data.frame(combined.filtered[1:32,])
```

```{r}
#png("hierachical clustering.png", width = 1000, height = 1000)
sampleTree = stats::hclust(as.dist(combined.filtered), method = "ward.D2");

# Plot the sample tree: Open a graphic output window of size 12 by 9 inches
# The user should change the dimensions if the window is too large or too small.
sizeGrWindow(12,9)
#pdf(file = "Plots/sampleClustering.pdf", width = 12, height = 9);
par(cex = 0.6);
par(mar = c(0,4,2,0))
plot(sampleTree, main = "Sample clustering to detect outliers", hang=-1,sub="", xlab="", cex.lab = 1.5, 
     cex.axis = 1.5, cex.main = 2)
#dev.off()


```



```{r}
#select clinical variables 

clinical_1<-subset(clinical_1, select = c('diag', 'Gender', 'Associated disease', 'Ascites at diagnosis', 'HVPG', 'whvp', 'PLAT_diag', 'BI_total_diag', 'Spleen', 'Fibroscan','No associated condition', 'Hematological associated condition', 'Associated cosnition HIV' ))
rownames(clinical_1)<-colnames(normalised_data)

#convert categorical variables to numeric levels 

#first conver the cat columns to factors 

clinical_1$diag<-as.factor(clinical_1$diag)
clinical_1$Gender<-as.factor(clinical_1$Gender)
clinical_1$`Associated disease`<-as.factor(clinical_1$`Associated disease`)
clinical_1$`Ascites at diagnosis`<-as.factor(clinical_1$`Ascites at diagnosis`)


#convert cate to numeric levels 

clinical_1$diag<-unclass(clinical_1$diag)
clinical_1$Gender<-unclass(clinical_1$Gender)
clinical_1$`Associated disease`<-unclass(clinical_1$`Associated disease`)
clinical_1$`Ascites at diagnosis`<-unclass(clinical_1$`Ascites at diagnosis`)

#convert character columsn to numeric
clinical_1$diag<-as.numeric(clinical_1$diag)
clinical_1$Gender<-as.numeric(clinical_1$Gender)
clinical_1$`Associated disease`<-as.numeric(clinical_1$`Associated disease`)
clinical_1$`Ascites at diagnosis`<-as.numeric(clinical_1$`Ascites at diagnosis`)
clinical_1$HVPG<-as.numeric(clinical_1$HVPG)
clinical_1$whvp<-as.numeric(clinical_1$whvp)
clinical_1$PLAT_diag<-as.numeric(clinical_1$PLAT_diag)
clinical_1$BI_total_diag <-as.numeric(clinical_1$BI_total_diag)
clinical_1$Spleen<-as.numeric(clinical_1$Spleen)
clinical_1$Fibroscan<-as.numeric(clinical_1$Fibroscan)

#clinical_1<-as.matrix(clinical_1)

```

#merge together the filtered table with the information from the Giannakis dataset
```{r}
# Re-cluster samples
sampleTree2 = stats::hclust(as.dist(combined.filtered), method = "ward.D2")
# Convert traits to a color representation: white means low, red means high, grey means missing entry
traitColors = numbers2colors(clinical_1, signed = FALSE);
sizeGrWindow(12,12)

# Plot the sample dendrogram and the colors underneath.
plotDendroAndColors(sampleTree2, traitColors,
                    groupLabels = names(clinical_1), 
                    main = "Sample dendrogram and trait heatmap",
                    addGuide = TRUE)
##stage 2.14 and stage 4.4 outliers 

```



```{r}
save(combined.filtered, trait_data, file = "WGCNA-input.RData")
```





#########################################
Network construction and module detection
#########################################

```{r}
# Allow multi-threading within WGCNA. This helps speed up certain calculations.
# At present this call is necessary for the code to work.
# Any error here may be ignored but you may want to update WGCNA if you see one.
# Caution: skip this line if you run RStudio or other third-party R environments. 
# See note above.

enableWGCNAThreads(nThreads = 8)# Load the data saved in the first part
#lnames = load(file = "WGCNA-input.RData");
#The variable lnames contains the names of loaded variables.
#lnames
```

```{r}
# Choose a set of soft-thresholding powers

powers = c(c(1:10), seq(from = 12, to=30, by=2))
# Call the network topology analysis function
sft = pickSoftThreshold(combined.filtered, powerVector = powers, verbose = 5, networkType = "signed")#using unsigned option
# Plot the results:
sizeGrWindow(9, 5)
par(mfrow = c(1,2));
cex1 = 0.9;
# Scale-free topology fit index as a function of the soft-thresholding power
plot(sft$fitIndices[,1], -sign(sft$fitIndices[,3])*sft$fitIndices[,2],
     xlab="Soft Threshold (power)",ylab="Scale Free Topology Model Fit, signed R^2",type="n",
     main = paste("Scale independence"));
text(sft$fitIndices[,1], -sign(sft$fitIndices[,3])*sft$fitIndices[,2],
     labels=powers,cex=cex1,col="red");
# this line corresponds to using an R^2 cut-off of h
abline(h=0.90,col="red")
# Mean connectivity as a function of the soft-thresholding power
plot(sft$fitIndices[,1], sft$fitIndices[,5],
     xlab="Soft Threshold (power)",ylab="Mean Connectivity", type="n",
     main = paste("Mean connectivity"))
text(sft$fitIndices[,1], sft$fitIndices[,5], labels=powers, cex=cex1,col="red")
#choosing power 5 to get a sclae free network
```



```{r}
# Choose a set of soft-thresholding powers

powers = c(c(1:10), seq(from = 12, to=30, by=2))
# Call the network topology analysis function
sft = pickSoftThreshold(combined.filtered, powerVector = powers, verbose = 5, networkType = "signed hybrid")#using unsigned option
# Plot the results:
sizeGrWindow(9, 5)
par(mfrow = c(1,2));
cex1 = 0.9;
# Scale-free topology fit index as a function of the soft-thresholding power
plot(sft$fitIndices[,1], -sign(sft$fitIndices[,3])*sft$fitIndices[,2],
     xlab="Soft Threshold (power)",ylab="Scale Free Topology Model Fit,unsigned R^2",type="n",
     main = paste("Scale independence"));
text(sft$fitIndices[,1], -sign(sft$fitIndices[,3])*sft$fitIndices[,2],
     labels=powers,cex=cex1,col="red");
# this line corresponds to using an R^2 cut-off of h
abline(h=0.9,col="red")
# Mean connectivity as a function of the soft-thresholding power
plot(sft$fitIndices[,1], sft$fitIndices[,5],
     xlab="Soft Threshold (power)",ylab="Mean Connectivity", type="n",
     main = paste("Mean connectivity"))
text(sft$fitIndices[,1], sft$fitIndices[,5], labels=powers, cex=cex1,col="red")
#choosing power 5 to get a sclae free network
```

```{r}
# here we define the adjacency matrix using soft thresholding with beta=6
#ADJ1=abs(cor(combined.filtered,use="p"))^14
# When you have relatively few genes (<5000) use the following code
#k=as.vector(apply(ADJ1,2,sum, na.rm=T))
# When you have a lot of genes use the following code
k=softConnectivity(datE=combined.filtered,power=16, type="signed")
# Plot a histogram of k and a scale free topology plot
sizeGrWindow(10,5)
par(mfrow=c(1,2))
hist(k)
scaleFreePlot(k, main="Check scale free topology\n")

```


```{r}
softPower = 16;
adjacency = adjacency(combined.filtered, power = softPower, type = "signed");
```


```{r}
# Turn adjacency into topological overlap
TOM = TOMsimilarity(adjacency, TOMType = "signed");
dissTOM = 1-TOM
```



```{r}
# Transform dissTOM with a power to make moderately strong connections more visible in the heatmap
plotTOM = dissTOM^16;
# Set diagonal to NA for a nicer plot
diag(plotTOM) = NA;
# Call the plot function
sizeGrWindow(9,9)
TOMplot(plotTOM, geneTree, moduleColors, main = "Network heatmap plot, all genes")
```


```{r}
library(gplots)
myheatcol = colorpanel(250,'red',"orange",'lemonchiffon')
TOMplot(plotTOM, geneTree, moduleColors, main = "Network heatmap plot, all genes", col=myheatcol)
```





```{r}
#automatic
net = blockwiseModules(combined.filtered, 
                       power = 14, 
                       corType= "pearson", 
                       networkType = "signed hybrid",
                       TOMType = "unsigned", 
                       minModuleSize = 30,
                       maxBlockSize = 17400,
                       reassignThreshold = 1e-6, 
                       deepSplit = 2, 
                       mergeCutHeight = 0.20, 
                       numericLabels = TRUE, 
                       pamRespectsDendro = FALSE,
                       saveTOMs = FALSE, 
                       verbose = 3)
```
```{r}
# open a graphics window
sizeGrWindow(15, 9)
# Convert labels to colors for plotting
mergedColors = labels2colors(net$colors)
# Plot the dendrogram and the module colors underneath
plotDendroAndColors(net$dendrograms[[1]], mergedColors[net$blockGenes[[1]]],
                    "Module colors",
                    dendroLabels = FALSE, hang = 0.03,
                    addGuide = TRUE, guideHang = 0.05)

```


```{r}
# Call the hierarchical clustering function
geneTree = flashClust(as.dist(dissTOM), method = "average");
# Plot the resulting clustering tree (dendrogram)
#sizeGrWindow(12,12)
plot(geneTree, xlab="", sub="", main = "Gene clustering on TOM-based dissimilarity",
labels = FALSE, hang = 0.07);

```


```{r}
###module detection#############
###set minimum module size
minModuleSize = 30;
# Module identification using dynamic tree cut:
dynamicMods = cutreeDynamic(dendro = geneTree, 
                            distM = dissTOM, 
                            deepSplit = 2, 
                            cutHeight = "tree",
                            pamRespectsDendro = FALSE,
minClusterSize = minModuleSize);
table(dynamicMods)
```


```{r}
# Convert numeric lables into colors
dynamicColors = labels2colors(dynamicMods)
table(dynamicColors)
# Plot the dendrogram and colors underneath
sizeGrWindow(8,6)
#pdf("gene_tree_colorsv2.pdf")
plotDendroAndColors(geneTree, dynamicColors, "Dynamic Tree Cut",
dendroLabels = FALSE, hang = 0.03,
addGuide = TRUE, guideHang = 0.05,
main = "Gene dendrogram and module colors")


#dev.off()
```


```{r}
##cluster modules together that their expression is similar
MEList = moduleEigengenes(combined.filtered, colors = dynamicColors)
# Calculate dissimilarity of module eigengenes
MEs = MEList$eigengenes
# Calculate dissimilarity of module eigengenes
MEDiss = 1-cor(MEs);
# Cluster module eigengenes
METree = hclust(as.dist(MEDiss), method = "average");
```




```{r}
####plot clustering of modules
sizeGrWindow(7, 6)
#pdf("Clustering of module eigengenes.pdf")
plot(METree, main = "Clustering of module eigengenes",
xlab = "", sub = "")
abline(h=0.25, col = "red")
#dev.off()
```



```{r}
####From this point on we can set the parameters to merge similar modules, if needed. 
####high value for merging, very small not merging.
MEDissThres = 0.25

# Plot the cut line into the dendrogram

# Call an automatic merging function
merge = mergeCloseModules(combined.filtered, dynamicColors, cutHeight = MEDissThres, verbose = 3)
# The merged module colors
mergedColors = merge$colors;
# Eigengenes of the new merged modules:
mergedMEs = merge$newMEs;
#dev.off()
```



```{r}
sizeGrWindow(12, 9)
diagnosis= as.data.frame(clinical_1$diag)
names(diagnosis)="diagnosis"
GS.diagnosis = as.numeric(cor(combined.filtered, diagnosis, use="p"))
GS.diagColor = numbers2colors(GS.diagnosis, signed = T)
#datColors = data.frame(moduleColorsAutomatic, GS.weightColor)[net$blockGenes[[blocknumber]], 
 #   ]
####plot the new merged modules
#pdf(file = "HDgeneDendro_merged_modules_0.1.pdf", wi = 9, he = 6)
plotDendroAndColors(geneTree, cbind(dynamicColors, mergedColors),
c("Dynamic Tree Cut", "Merged dynamic"),
dendroLabels = FALSE, hang = 0.03,
addGuide = TRUE, guideHang = 0.05)
#abline(h=MEDissThres, col = "red")
#dev.off()
```


```{r}
# Rename to moduleColors
moduleColors = mergedColors
# Construct numerical labels corresponding to the colors
colorOrder = c("grey", standardColors(50));
moduleLabels = match(moduleColors, colorOrder)-1;
MEs = mergedMEs;


```



```{r}
nGenes=ncol(combined.filtered)
nSamples=nrow(combined.filtered)
MEs0=moduleEigengenes(combined.filtered,moduleColors)$eigengenes
MEs=orderMEs(MEs0)

moduleTraitCor = cor(MEs, clinical_1, use = "p");
moduleTraitPvalue = corPvalueStudent(moduleTraitCor, nSamples);
```

```{r}
sizeGrWindow(12, 12)
# Plot the relationships among the eigengenes and the trait
plotEigengeneNetworks(MEs, "", marDendro = c(0, 4, 1, 2), marHeatmap = c(3, 
    4, 1, 2), cex.lab = 0.8, xLabelsAngle = 90)
```




```{r}
# Will display correlations and their p-values
textMatrix <- paste(signif(moduleTraitCor, 2), "\n(",
                    signif(moduleTraitPvalue, 1), ")", sep = "");
                    dim(textMatrix) = dim(moduleTraitCor)
                    par(mar = c(6, 8.5, 3, 3));
```


```{r}
sizeGrWindow(50,50)
pdf("thres_modules_hd_traits.pdf")
# Will display correlations and their p-values
textMatrix = paste(signif(moduleTraitCor, 2), "\n(",
signif(moduleTraitPvalue, 1), ")", sep = "");
dim(textMatrix) = dim(moduleTraitCor)
par(mar = c(6, 8.5, 3, 3));
# Display the correlation values within a heatmap plot
labeledHeatmap(Matrix = moduleTraitCor,
xLabels = names(clinical_1),
yLabels = names(MEs),
ySymbols = names(MEs),
colorLabels = FALSE,
colors = blueWhiteRed(50),
textMatrix = textMatrix,
setStdMargins = FALSE,
cex.text = 0.4,
zlim = c(-1,1),
main = paste("Module-trait relationships"))
dev.off()

```

```{r}
##calculate intramosular connectivity 
#ADJ1=abs(cor(datExpr,use="p"))^6
Alldegrees1=intramodularConnectivity(adjacency, moduleColors, scaleByMax = FALSE)
head(Alldegrees1)
```


```{r}
colorlevels=unique(moduleColors)
sizeGrWindow(9,6)
par(mfrow=c(2,6))
par(mar = c(4,5,3,1))
for (i in c(1:12))
{
whichmodule=colorlevels[[i]];
restrict1 = (moduleColors==whichmodule);
verboseScatterplot(Alldegrees1$kWithin[restrict1],
GS.diagnosis[restrict1], col=moduleColors[restrict1],
main=whichmodule,
xlab = "Connectivity", ylab = "Gene Significance", abline = TRUE)
}
```

```{r}
colorlevels=unique(moduleColors)
sizeGrWindow(9,6)
par(mfrow=c(2,5))
par(mar = c(4,5,3,1))
for (i in c(13:22))
{
whichmodule=colorlevels[[i]];
restrict1 = (moduleColors==whichmodule);
verboseScatterplot(Alldegrees1$kWithin[restrict1],
GS.diagnosis[restrict1], col=moduleColors[restrict1],
main=whichmodule,
xlab = "Connectivity", ylab = "Gene Significance", abline = TRUE)
}
```


```{r}
##module membership 

###signedKME

hobag=signedKME(combined.filtered, MEs, outputColumnName="kME", corFnc="cor", corOptions= "use = 'p'")
#write.table(hobag, file='hobag.csv', sep='\t')

#ADJ1=abs(cor(combined.filtered,use="p"))^14
#Alldegrees1=intramodularConnectivity(ADJ1, colorh1)
#write.table(Alldegrees1, file='connectivity.csv', sep='\t')


```


```{r}

colorOfColumn = substring(names(hobag), 4)
par(mfrow = c(2, 4))
selectModules = c("lightpink3", "coral1", "darkviolet", "darkslateblue","lightcyan1")
par(mfrow = c(2, length(selectModules)/2))
for (module in selectModules) {
    column = match(module, colorOfColumn)
    restModule = moduleColors == module
    verboseScatterplot(hobag[restModule, column], GS.diagnosis[restModule], xlab = paste("Module Membership ", 
        module, "module"), ylab = "GS.diagnosis", main = paste("kME.", module, 
        "vs. GS"), col = module)
}
```


```{r}

colorOfColumn = substring(names(hobag), 4)
par(mfrow = c(2, 4))
selectModules = c("plum2", "navajowhite2", "plum", "darkorange","darkolivegreen", "lightpink4", "palevioletred3", "skyblue")
par(mfrow = c(2, length(selectModules)/2))
for (module in selectModules) {
    column = match(module, colorOfColumn)
    restModule = moduleColors == module
    verboseScatterplot(hobag[restModule, column], GS.diagnosis[restModule], xlab = paste("Module Membership ", 
        module, "module"), ylab = "GS.diagnosis", main = paste("kME.", module, 
        "vs. GS"), col = module)
}
```



```{r}
#FilterGenes= abs(Alldegrees1)> 0.2 & abs(hobag$kMElightpink3)> 0.8
#FilterGenes= abs(hobag$kMElightpink3)> 0.8 & abs(Alldegrees1)> 0.6
FilterGenes= (hobag$kMEdarkorange)>= 0.7 & abs(Alldegrees1$kWithin)>= 10
table(FilterGenes)
```




```{r}
# Define variable time containing the stage column of trait data
diagnosis = as.data.frame(clinical_1$diag);
names(diagnosis) = "diagnosis"
# names (colors) of the modules
modNames = substring(names(MEs), 3)

geneModuleMembership = as.data.frame(cor(combined.filtered, MEs, use = "p"));
MMPvalue = as.data.frame(corPvalueStudent(as.matrix(geneModuleMembership), nSamples));

names(geneModuleMembership) = paste("MM", modNames, sep="");
names(MMPvalue) = paste("p.MM", modNames, sep="");

geneTraitSignificance = as.data.frame(cor(combined.filtered, diagnosis, use = "p"));
GSPvalue = as.data.frame(corPvalueStudent(as.matrix(geneTraitSignificance), nSamples));

names(geneTraitSignificance) = paste("GS.", names(diagnosis), sep="");
names(GSPvalue) = paste("p.GS.", names(diagnosis), sep="");
```


```{r}
# Create the starting data frame containing gene id , module they are present in, significance and correlation for each gene
geneInfo0 = data.frame(Gene.Symbol = colnames(combined.filtered),
                      moduleColor = moduleColors,
                      geneTraitSignificance,
                      GSPvalue)

##selecting modules with higher than 0.6 correlation
darkorange_module<-subset(geneInfo0,moduleColor=="darkorange")


#add in kme column and the intramodular connectivity 
darkorange_module$kMEdarkorange = hobag$kMEdarkorange[match(row.names(darkorange_module), row.names(hobag))]
darkorange_module$kWithin<-  Alldegrees1$kWithin[match(row.names(darkorange_module), row.names(Alldegrees1))]

darkorange_module<-subset(darkorange_module, p.GS.diagnosis<=0.01 & abs(GS.diagnosis)>=0.6 & kWithin >=50)
write.table(darkorange_module$Gene.Symbol, "topgenes.txt", na ="", row.names=FALSE,  sep='\t', quote=FALSE)
```



```{r}
#ranking for gsea 
darkorange_module$ranking<-darkorange_module$GS.diagnosis*-log10(darkorange_module$p.GS.diagnosis)
```


```{r}
#performing over representation analysis for pathways using KEGG 
#creating dataframe with ensemble id, entrez id and gene symbols.
gene.df <- bitr(ensemble_gene_list$V1, fromType = "ENSEMBL",
        toType = c("ENTREZID", "SYMBOL"),
        OrgDb = org.Hs.eg.db)

#over representation analysis using KEGG 
over_rep_pathways <- data.frame(enrichKEGG(gene= gene.df$ENTREZID,
                                organism     = 'hsa',
                                pvalueCutoff = 0.05))
#print the result
head(over_rep_pathways)
```

```{r}

```


###################################
Community clustering
###################################


```{r}
library(igraph)



```




###################################
Network visualization 
###################################

```{r}

# Create a list of all the available organisms for biomaRt annotation
list <- panev.biomartSpecies(string = NULL)
# Look for a specific organism matching a search string for biomaRt annotation
list <- panev.biomartSpecies(string = "Human")
#select the correct organism fo interest
biomart.species.bos <- as.character(list[1,1])
# Prepare the dataset for panev.network function converting gene name from ensembl to entrez id
ensemble_id<-getBM(attributes=c('ensembl_gene_id','entrezgene_id'),
                filter='entrezgene_id',
                values=green_module_genes$Gene.Symbol,
                mart=ensembl)
#create dataframe of ensemble gene id 
ensemble_gene_list<-data.frame(ensemble_id$ensembl_gene_id)
#assign columnnames 
colnames(ensemble_gene_list)<-c("ensemble_id")
#export the ensemble gene id as a text file
write.table(ensemble_gene_list,"ensemble gene list.txt",row.names = F,quote = F)

#ensemble_gene_list<-read.table("ensemble gene list.txt",header = F,stringsAsFactors = F)
# Preparation of the dataset for panev.network function, converting gene name from entrez to ensembl id
genelist.converted <- panev.dataPreparation(in.file = "ensemble gene list.txt", 
                                          gene_id = "ensembl", 
                                          biomart.species = biomart.species.bos)
#export the dataframe containing entrex id, ensemble gen id and gene symbols 
write.table(genelist.converted,"data.txt",row.names = F,quote = F)
#get the pathway list from KEGG
list <- panev.pathList(string = NULL)#path:map04146 path:map00730 path:map00740 path:map00750 path:map01524 path:map02010 path:map04514
#Idenify the pathways of interest ( were selected using information from functional annoation clustering DAVID and ORA for pathways)
FL.gene <- c("path:map04146", "path:map00730", "path:map00740", "path:map00750","path:map01524","path:map02010","path:map04514")
write.table(list,"list.txt")

# Create a list of all available organisms in KEGG
list <- panev.speciesCode(string = "human")
#select appropriate organism
KEGG.species.bos <- as.character(list[1,2])
#Perform PANEV
panev.network(in.file = "data.txt", 
              out.file = "example", 
              species = KEGG.species.bos, 
              FL = FL.gene, 
              levels = 2)
#Export the files to folder PANEV_RESULTS_example. The HTML file can be used to visulaize the network
genes.1L <- read.table("C:\\Users\\HP\\Desktop\\Network Biology\\project\\Colon\\MicroRNA-Gene-Network-Colon\\Data\\PANEV_RESULTS_example\\1Lgenes.txt", header = TRUE)
```
Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
